\begin{question}{6}
Are the two sets of state-space equations

\begin{align}
  \dot{X}(t) &=
  \begin{bmatrix}
    2 & 2 & 1 \\
    0 & 2 & 2 \\
    0 & 0 & 1
  \end{bmatrix} X(t)
  +
  \begin{bmatrix}
    1 \\ 1 \\ 0
  \end{bmatrix}
  u(t),
  \quad
  y(t) =
  \begin{bmatrix}
    1 & -1 & 0
  \end{bmatrix} \label{eq:q6_sys_a}
  \\ \nonumber \\
  \dot{X}(t) &=
  \begin{bmatrix}
    2 & 1 &  1 \\
    0 & 2 &  1 \\
    0 & 0 & -1
  \end{bmatrix} X(t)
  +
  \begin{bmatrix}
    1 \\ 1 \\ 0
  \end{bmatrix}
  u(t),
  \quad
  y(t) =
  \begin{bmatrix}
    1 & -1 & 0
  \end{bmatrix} \label{eq:q6_sys_b}
\end{align}
\noindent equivalent? Zero-state equivalent?
\end{question}

\noindent \textbf{a)} For equivalence, we must show that the $A$ matrix of both
systems have the same eigenvalues.

Starting with the system given by Equation \ref{eq:q6_sys_a}, the eigenvalues
are

\begin{align}
  [s \mathbb{I} - A]^{-1} &=
  \begin{bmatrix}
    s-2 & -1  & -2 \\
    0   & s-2 & -2 \\
    0   & 0   & s-1
  \end{bmatrix} \label{eq:q6_sys_a_inv} \\
  &= (s-2)^2 (s-1) \nonumber \\
  &= 0 \nonumber \\
  \therefore
  \lambda_{1,2,3} &= 2, 2, 1 \label{eq:q6_sys_a_ev}
\end{align}

\noindent and the eigenvalues for the system given by Equation \ref{eq:q6_sys_b}
are

\begin{align}
  [s \mathbb{I} - A]^{-1} &=
  \begin{bmatrix}
    s-2 & -1  & -1 \\
    0   & s-2 & -1 \\
    0   & 0   & s+1
  \end{bmatrix} \label{eq:q6_sys_b_inv} \\
  &= (s-2)^2 (s+1) \nonumber \\
  &= 0 \nonumber \\
  \therefore
  \lambda_{1,2,3} &= 2, 2, -1 \label{eq:q6_sys_b_ev}
\end{align}

Equations \ref{eq:q6_sys_a_ev} and \ref{eq:q6_sys_b_ev} show that the
eigenvalues of the two systems are different. Therefore, the two sets of
state-space equations are not equivalent.

\noindent \textbf{b)} For zero-state equivalence, we must show that the two sets
of state-space equations have the same transfer matrix. The transfer matrix is
given by

\begin{equation} \nonumber
  \dfrac{Y(s)}{U(s)} = C[s\mathbb{I}-A]^{-1}B + D
\end{equation}

The $C$, $B$, and $D$ are the same for both systems which means in order for the
two sets of state-space equations to be zero-state equivalent then the
$[s\mathbb{I}-A]^{-1}$ must be equivalent. As is shown in Equations
\ref{eq:q6_sys_a_inv} and \ref{eq:q6_sys_b_inv}, these two matrices are
\textit{not} the same. Therefore, the two sets of state-space equations are not
zero-state equivalent.
